From Education to Entrepreneurship

### 2014-12-06 ExtraCharts_index/ExtraCharts.Rmd
Removed unnecessary charts and added website text

---
title: 'From Education to Entrepreneurship'
author: "Sam"
date: "November 20, 2014"
output: html_document
---

### Under construction, but here's a preview

```{r echo =FALSE, cache=FALSE, include=TRUE, results='asis', warning=FALSE, error=FALSE, message=FALSE}
library(ggvis)
library("devtools")
library(googleVis)
library(countrycode)
library(repmis)
library(reshape2)
library(RJSONIO)
library(shiny)
library(httpuv)

@@

CD <- repmis::source_data("https://raw.githubusercontent.com/SamDund/Assign2Education/master/GEMData/CompleteData.csv", header = TRUE, na.strings = "NA")

# Set Year column as a date
CD$Year <- as.Date(as.character(CD$Year), format = "%Y")

# Dropp X column
CD$X <- NULL

R <- gvisMotionChart(CD, idvar = "Country", timevar = "Year")

print(R, tag = 'chart')
```

>>>>

---
title: "Untitled"
author: "Sam"
date: "December 6, 2014"
output: html_document
---

@@

### 2014-12-06 index.Rmd
Removed unnecessary charts and added website text

---
title: 'From Education to Entrepreneurship'
author: "Sam"
date: "November 20, 2014"
output: html_document
---

### Under construction, but here's a preview

```{r echo =FALSE, cache=FALSE, include=TRUE, results='asis', warning=FALSE, error=FALSE, message=FALSE}
library(ggvis)
library("devtools")
library(googleVis)
library(countrycode)
library(repmis)
library(reshape2)
library(RJSONIO)
library(shiny)
library(httpuv)

# Import GEM data frame
PerceivedOpportunities <- repmis::source_data("https://raw.githubusercontent.com/SamDund/Assign2Education/master/GEMData/PerceivedOpportunities.csv", header = TRUE, cache = FALSE, na.strings = "-")

## Add country codes and place new column at beginning of the data frame
# Create a vector of country codes

D2 <- countrycode(PerceivedOpportunities$Country, "country.name", "iso2c")

# Create a new column and insert the country code vector
PerceivedOpportunities$new.col <- D2

# Reorder columns so country code is first
D3 <- PerceivedOpportunities[,c(15,1:14)]

# Rename first column
D4 <- plyr::rename(x = D3, 
                   replace = c("new.col" = "iso2c"))

# Remove X's in D4 year columns
names(D4) <- gsub("X", "", names(D4))

# Melt D4 df
D6 <- melt(data = D4,
                  id.vars = c("Country", "iso2c"),
                  measure.vars = c("2001", "2002", "2003", "2004", "2005", "2006",
                                   "2007", "2008", "2009", "2010"))

# Change column titles to  year and PerceivedOpportunities
names(D6) <- gsub("value", "PerceivedOpportunities", names(D6))    
names(D6) <- gsub("variable", "Year", names(D6))

# Set columns as numeric
D6[,"PerceivedOpportunities"] <- as.numeric(D6[,"PerceivedOpportunities"])

# Save cleaned df
D7 <- D6

# Create country vector to subset
myvars2 <- c('US','FR','DE','JP','GB')

# Subset D6
D8 <- subset(D6, iso2c %in% myvars2)

# Create a scatterplot
D8 %>% 
  ggvis(~Year, ~PerceivedOpportunities) %>%
  layer_points(fill = ~factor(Country)) %>%
  group_by(Country)

D8 %>%
  ggvis(~Year, ~PerceivedOpportunities) %>%
  layer_points(fill = ~factor(Country)) %>%
  group_by(Country)

```

```{r echo =FALSE, cache=FALSE, include=TRUE, results='asis', warning=FALSE, error=FALSE, message=FALSE}

@@

>>>>

---
title: 'From Education to Entrepreneurship'
author: "Sam Dundon and Thierry Racaud"
date: "December 6, 2014"
output: html_document
---

**Key Question**
To what extent do teaching methods supporting self-confidence affect the rate of entrepreneurship in OECD countries?

We have drawn on publicly availabile data from the Global Entrepreneurship Monitor (GEM) National Entrepreneurship Survey (NES) and Adult Population Survey (APS) to create graphic visualizations of participants' responses to surveys about entrepreneurship.

The following interactive chart can be utilized to see the relationship between the variables we investigated. Among other features, the independent and dependent variables can be selected to see the relationship between each of the variables.

```{r echo =FALSE, cache=FALSE, include=TRUE, results='asis', warning=FALSE, error=FALSE, message=FALSE}
library(ggvis)
library(devtools)
library(googleVis)
library(countrycode)
library(repmis)
library(reshape2)
library(RJSONIO)
library(shiny)
library(httpuv)

@@

As indicated in the chart, our analysis investigated the variation among OECD countries in each of the following variables.
